---
title: "MSNA Sudan 2024 RMS Indicators"
institute: "Global Survey Team"
date: "19 November 2024"
format: unhcr-revealjs
---

```{r}
source("msna_sudan_2024_rms.R")
```


# Impact indicators {.slide-blue}

## 

```{r}
impact2_2_plot
```

Includes access to: habitable housing, basic facilities, and security from natural hazards

## 

```{r}
impact2_3_plot
```

Measures the share of households that accessed health care among those that needed it.

# Outcome indicators {.slide-blue}

##

```{r}
outcome8_2_plot
```

Any type of cooking fuel and technology meeting the WHO set standards on indoor air emissions

## 

```{r}
outcome9_2_plot
```

Clean fuels for lighting include electricity, renewable energy, fuels considered clean for health and battery flashlights.

## 

```{r}
outcome12_1_plot
```

Basic drinking water services: drinking water from an improved source, with collection time max. 30 minutes

## 

```{r}
outcome12_2_plot
```

Safe household toilets: improved sanitation facilities, emptied safely and not shared with other households.

## 

```{r}
outcome13_2_plot
```

Note: Different wording means that the indicator here is not quite the same as in the RMS.

## 

```{r}
outcome16_2_plot
```

Note: Here we only capture national social assistance if it was one of three main income sources.

## Notes

- Some indicator calculation has been adapted to use available questions

- All indicators calculated here are at the household-level, where some corresponding RMS indicators are individual-level